A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-04-24 paper/paper1/ms.tex
compress figures, tables and text to eliminate whitespace

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.7\linewidth]{figures/TESS_HAT-P-67b_overview.png}
    \caption{Overview of all available TESS Sectors showing 24 full or partial transits with 34 visits with HPF (vertical gray bars), 7 of which coincide with transits.  The rest of the visits sample out-of-transit phases.  The 8 HPF visits between BTJD 2050 and 2690 are not shown.}
    \label{fig:TESSoverview}
\end{figure*}

@@

\subsection{HPF analysis I: RV fitting}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT-P-67b_rv.pdf}
    \caption{RV orbit fit including both HPF and Keck HIRES data points.}
    \label{fig:RVfit}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=5cm]{figures/centroid_overview10833.png} }
    \hskip-3em
    \subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
    \caption{Line centroid positions of the  10830 triplet.  \emph{left}: The overview panel shows a slight blueshift relative to the stellar restframe, and a weak excess blueshift trend after planet egress. \emph{right:} The detailed zoom-in of the in-transit phase shows a redshift relative to the planet restframe at ingress and a blueshift relative to the planet restframe near egress.  The line-of-sight velocity distribution of 2-3 \AA means that the gas distribution exhibits both advancing and receding lobes at all phases other than post-egress.}
    \label{fig:example}
\end{figure}

@@

\begin{deluxetable}{lLLCR}
    \tablewidth{0pc}
    \tabletypesize{\scriptsize}
    \tablecaption{
        Coarse Inflation Timescales for Hot Jupiters
        \label{tabHeSM}
    }
    \tablehead{
        \colhead{Planet}   &
        \colhead{Mass} &
        \colhead{Radius} &
        \colhead{Eq. Temp.} &
        \colhead{$\tau_\mathrm{infl}$} \\
        \colhead{}   &
        \colhead{$M_\mathrm{Jup}$} &
        \colhead{$R_\mathrm{Jup}$}   &
        \colhead{K} &
        \colhead{Myr}
    }
    \startdata
    \input{tables/tab_HeSM.tex}
    \enddata
    \tablecomments{Inflation timescale assumes $\epsilon=0.01$.}
\end{deluxetable}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=0.98\linewidth]{figures/TESS_HAT-P-67b_overview.png}
    \caption{Overview of all available TESS Sectors showing 24 full or partial transits with 34 visits with HPF (vertical gray bars), 7 of which coincide with transits.  The rest of the visits sample out-of-transit phases.  The 8 HPF visits between BTJD 2050 and 2690 are not shown.  Note the large time breaks between some consecutive panels, which correspond roughly to the duration of a TESS sector.}
    \label{fig:TESSoverview}
\end{figure*}

@@

@@

\subsection{HPF analysis I: RV fitting}
\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT-P-67b_rv.pdf}
    \caption{RV orbit fit including both HPF and Keck HIRES data points.}
    \label{fig:RVfit}
\end{figure}

@@

@@

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=5cm]{figures/centroid_overview10833.png} }
    \hskip-3em
    \subfloat{\includegraphics[width=4cm]{figures/centroid_inset10833.png}}
    \caption{Line centroid positions of the  \ion{He}{1} 10830 \AA~ feature.  \emph{left}: The overview panel shows a slight blueshift relative to the stellar restframe, and a weak excess blueshift trend after planet egress. \emph{right:} The detailed zoom-in of the in-transit phase shows a redshift relative to the planet restframe at ingress and a blueshift relative to the planet restframe near egress.  The line-of-sight velocity distribution of 2-3 \AA~ means that the gas distribution exhibits both advancing and receding lobes at all phases other than post-egress.}
    \label{fig:example}
\end{figure}

@@

\begin{deluxetable}{lLLCR}
    \tablewidth{0pc}
    \tabletypesize{\scriptsize}
    \tablecaption{
        Coarse Inflation Timescales for Hot Jupiters
        \label{tabHeSM}
    }
    \tablehead{
        \colhead{Planet}   &
        \colhead{Mass} &
        \colhead{Radius} &
        \colhead{$T_\mathrm{eq}$} &
        \colhead{$\tau_\mathrm{infl}$} \\
        \colhead{}   &
        \colhead{$M_\mathrm{Jup}$} &
        \colhead{$R_\mathrm{Jup}$}   &
        \colhead{K} &
        \colhead{Myr}
    }
    \startdata
    \input{tables/tab_HeSM.tex}
    \enddata
    %\tablecomments{Inflation timescale assumes $\epsilon=0.01$.}  Not true, we use the empirical estimate
\end{deluxetable}
